eba_sims_data

### 2020-05-24 src/eba_sims_w_data.Rmd
costfunction into savingsfunction + first functions for storage sustainability analysis

```{r}
p <- 0.031
price_ratio <- 200
surface <- cost_surface(p, price_ratio)
plot_surface(surface, price_ratio, p)
plot_interactive_surface(surface)
```

>>>>

```{r savings effect, echo = FALSE}
p <- actual.deferral.rate
response.rate <- 1 - 1/10  # 10 invites -> 1 donor
invite.price <- 0.5  # Guess
deferral.price <- 30  # Guesstimate
savings <- savings_effect(p, response.rate, invite.price, deferral.price)

# Alternative p for comparison
p2 <- 0.1
alt.p <- savings_effect(p2, response.rate, invite.price, deferral.price)
```

```{r plot savings}
savings.df <- data.frame(savings = savings, alt = alt.p)
p <- ggplot(data = savings.df, aes(x = seq(0, 100, 1), y = -1*savings, color = "savings")) + 
  geom_line() +
  geom_line(aes(x = seq(0, 100, 1), y = -1*alt.p, color = "alt.p")) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Savings as a function of True Positive Rate",
       subtitle = "p = 0.031 and p = 0.1, response.rate = 0.9, invite.price = 0.5, deferral.price = 30",
       y = "Savings (€)",
       x = "TPR") +
  geom_text(aes(x = 100, y = 0.9, label = "p = 0.031", color = "savings")) +
  geom_text(aes(x = 100, y = 3.5, label = "p = 0.1", color = "alt.p"))

p
```

```{r deprecated_roc_space, include = FALSE}
# DEPRECATED!!! WORKS BUT IS INCORRECT. DO NOT USE.
p <- 0.031
price_ratio <- 13.683
surface <- cost_surface(p, price_ratio)
plot_surface(surface, price_ratio, p)
plot_interactive_surface(surface)
```

# Storage level simulation
```{r storage level}
# Create "pool series" based on the following "selections"
# We designate 5 different levels for donation intervals to approximate personalized donation intervals
# This is a "male pool" in that we set the intervals at 30, 40, 60, 70 and 90 days (below and above the current)
# We guess that those interval categories appear at rates 8, 12, 50, 20 and 10 percent
# We run the series for 1 year (365 days)
# We have a pool of 1000 invitees
# To simplify, it is furthermore assumed that invites are sent with 100% response rate at earliest eligibility

pool.series <- generate_pool_series(5, c(0.08, 0.12, 0.5, 0.20, 0.10), 1000, 365, c(30, 40, 60, 70, 90))
# TODO: Non-discretize the above (build on distributions)

# Let's simulate a 1000 realities with these parameters and find the worst case scenario
realities.matrix <- matrix(, nrow = 1000, ncol = 365)
for(i in 1:1000){
  pool.series <- generate_pool_series(5, c(0.08, 0.12, 0.5, 0.20, 0.10), 1000, 365, c(30, 40, 60, 70, 90))
  series <- colSums(pool.series)
  realities.matrix[i, ] <- series
}

# Find worst cases
worsts <- c()
for(i in 1:1000){
  worst <- min(realities.matrix[i, ][90:365])
  worsts <- c(worsts, worst)
}
```
